The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-15 paper.tex
update

 \Cref{fig__profile} shows the profiles) cut at the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
 The temperature profile indicates that most of the region between the forward shock and the turbulent region\
 is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}

 originally driven by an oblique bipolar jets emanating from the GC 12.39 million years ago,\
 and significantly stretched by the stratified atmosphere afterwards.

@@

>>>>

 The left column of \Cref{fig__profile} shows the profiles cut at\
 the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
 The temperature profile in the left column indicates that\
 most of the region between the forward shock and the turbulent region\
 is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}.

 Followed by the forward shock is a turbulent and high temperature ($\sim2$ keV) plasma.\
 By observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky, Miller& Bregman (2012)\
 found that the ratio between O viii and O vii\
 column densities is enhanced for sight lines that pass through\
 the Fermi bubbles, indicating gas temperature of a few times keV\
 inside the bubbles.

 % Reverse shock

@@

 %originally driven by an oblique bipolar jets emanating from the GC 12.39 million years ago,\
 %and significantly stretched by the stratified atmosphere afterwards.
